### 2017-10-16 mcmc.tex
edits to autocorr section

Given this pdf $p(\pars)$, we can define \emph{expectation values}
$E_{p(\pars)}[\pars]$
for $\pars$ or for any quantity that can be expressed as a function $g(\pars)$
of $\pars$:
\begin{eqnarray}
E_{p(\pars)}[\pars] &\equiv& \int \pars\,p(\pars)\,\dd \pars
\\
E_{p(\pars)}[g(\pars)] &\equiv& \int g(\pars)\,p(\pars)\,\dd \pars
\quad ,
\end{eqnarray}
where again the integrals are implicitly definite integrals over the
entire domain
of $\pars$ (all the parts of $\pars$ space in which $p(\pars)$ is finite) and the
integrals are multi-dimensional if $\pars$ is multi-dimensional.
These expectation values are the mean values of $\pars$ and $g(\pars)$ under
the pdf.  A good sampling---and really this is the definition of a good
sampling---makes the sampling approximation to these integrals
accurate.
With a good sampling $\setof{\pars_k}_{k=1}^K$ the integrals get replaced
with sums over samples $\pars_k$:
\begin{eqnarray}
E_{p(\pars)}[\pars] &\approx& \frac{1}{K}\,\sum_{k=1}^K \pars_k
\\
E_{p(\pars)}[g(\pars)] &\approx& \frac{1}{K}\,\sum_{k=1}^K g(\pars_k)
\quad .
\end{eqnarray}
That is, a sampling is good when any expectation value of interest is
accurately computed via the sampling approximation.
The word ``accurately'' here translates into some kinds of theorems
about limiting behavior; the general idea is that the sampling
approximation becomes exact as $K$ goes to infinity.
The size $K$ of the sampling you need \emph{in practice} will depend
on the expectations you want to compute, and the accuracies you need.

@@

\Needspace{7\baselineskip}
\section{Convergence}\label{sec:convergence}%
\nopagebreak%
A key question for an \MCMC\ operator---\emph{the} key question in some
sense---is \emph{how long to run} to be sure of having reliable
results.
It is disappointing and annoying to many that there is no extremely
simple and reliable answer to this question.\note{There is very good
  coverage of most of the points in this \sectionname, and more, in a
  set of lecture notes by Patrick Lam up at
  \url{http://www.people.fas.harvard.edu/~plam/teaching/methods/convergence/convergence_print.pdf}.}

The reason that there is no simple answer is that you can't really
ever know that you have sampled the full posterior pdf, and the reason
for \emph{that} is that if you \emph{could} know that, you would also
be able to solve the famously difficult discrete optimization
problem.\note{Famously, there is ``no free lunch''
  \citep{nofreelunch}: You can't find the global optimum of a general
  optimization problem without exhaustive search of all possibilities.
  This is very closely related---somehow---to the difficulty of sampling.}
Another way to put it is that you might have two modes---two separated
regions of substantial total probability---in the posterior pdf that
are both important but separated by a large region of low probability.
If you are using a simple sampler, you could sample one of these modes
very well but the sampler will take effectively infinite time to find
the other mode.
Any test of convergence would be passed, but in fact the sampling
would be incomplete and not representative.
That is, knowing that you have a complete and representative sampling
is effectively impossible.

@@

The above heuristics can be made more precise (in terms of the amount
of deviation one expects between the means and variances, say, of two
disjoint subsets of the chain.
The premier tool for making this heuristic precise, however, is to
look at the \emph{autocorrelation time} of the chain.
In general, when one has a sequence $(\pars_1, \pars_2, \theta_3, \cdots)$
generated by a Markov Process in the $\pars$ space, nearby points in
the sequence will be similar, but sufficiently distant points will not
``know about'' one another;
the autocorrelation function measures this.

More formally,

The autocorrelation function $C_g$ is defined by
\begin{eqnarray}
C_g(\Delta) &\equiv& \frac{E[(g(\pars_k)-\mu_g)\,(g(\pars_{k+\Delta})-\mu_g)]}
                          {E[(g(\pars)-\mu_g)^2]}
\label{eq:autocorrelationfn}\\
\mu_g &=& E[g(\pars)]
\quad ;
\end{eqnarray}
where $g(\pars)$ is a scalar valued function of the parameters, and $\Delta$
is a lag (difference in index number) between points in the chain.
In other words, \equationname~(\ref{eq:autocorrelationfn}) is the covariance
of points in the chain separated by $\Delta$ steps, taken relative to the
variance.
In the above equation, the assumption is that the samples $\pars_k$ are
given in the order that they were generated by the \MCMC\ algorithm.
By construction
\begin{eqnarray}
C_g(0) &=& 1
\\
\lim_{\Delta\rightarrow\infty} C_g(\Delta) &=& 0
\quad ,
\end{eqnarray}
and by definition, the autocorrelation ``time'' $\tau$ is
\begin{eqnarray}
\tau_g = 1 + 2\,\sum_{\Delta = 1}^{\infty} C_g(\Delta)
\label{eq:autocorrelationtime}\quad.
\end{eqnarray}
Heuristically, the autocorrelation time is the number of samples you
need to take before you get a new independent sample.
More precisely, the autocorrelation time is the factor by which you
have to reduce the number of samples when you compute the variance on
a sampling-based expectation value estimate.

That is, if the expectation value $E[g]$ is computed by the sampling
approximation given in \equationname~(\ref{eq:expectationvalue}),
there is an uncertainty on that expectation given by
\begin{eqnarray}
  \Var[E_{p(\pars)}[g(\pars)]] &=& \frac{\tau_g}{K}\,\Var_{p(\pars)}[g(\pars)]
  \\
  &\approx& \frac{\tau_g}{K^2}\,\sum_{k=1}^K \left(g(\pars_k) -
    E_{p(\pars)}[g(\pars)]\right)^2
  \quad,
\label{eq:tauvar}
\end{eqnarray}
where we are being a bit loose with terminology because this is the
variance not on $E_{p(\pars)}[g(\pars)]$ but on our sampling-based
\emph{estimator} for
$E_{p(\pars)}[g(\pars)]$, and the $E_{p(\pars)}[g(\pars)]$ inside the sum is
that estimator too.
It is slightly off-topic here, but related to this, if you have a long
chain of length $K$ and with autocorrelation time $\tau$ and you thin
the chain down to every $\tau$th sample (instead of using all $K$
samples), you will get just as good sampling-based estimates as if you
had used all $K$ samples.

It is also worth noting that there is not just one autocorrelation function or
autocorrelation time for an \MCMC\ chain.
Instead, there is an autocorrelation time $\tau_g$ for every function
$g(\pars)$ and these will, in general, be different.
Therefore, the autocorrelation time used in \equationname~(\ref{eq:tauvar}) is
the time computed on the chain of $g(\pars)$ values instead of the
autocorrelation time for $\pars$.

A sampler with a smaller autocorrelation time is just better; you have
to do fewer $f(\pars)$ calls per independent sample, and you have to
run less time to get accurate sampling-based integral estimates.
A sampler that takes an independent sample every time would have an
autocorrelation time of unity, which is the best possible value; this
optimal sampling is only possible for problems where the sampling is
analytic (for example if the posterior is perfectly Gaussian with
known mean and variance).
In general, the best sampler will be different for different problems, and we
will (below; \sectionname~\ref{sec:methods}) tune the samplers we have to do
the best on the problems we have; this tuning will also be problem-specific.
There are many heuristic bases on which different samplers might be
compared or tuned, but fundamentally it is lower autocorrelation time
that separates good samplers from bad ones and is the ultimate basis
on which we compare performance.\note{%
  We sometimes see \MCMC\ methods compared according to burn-in times,
  which, for one, depends strongly on initialization, and, for two,
  depends strongly on tuning and dynamics.  Similarly we often see
  comparisons in terms of acceptance ratio.  In principle the only
  question is how precise are one's inferences given a certain amount
  of computation.  This is set by the autocorrelation time and (pretty
  much) nothing else, for reasonably converged chains.  In the real
  world, of course, one must add to the CPU time the investigator time
  spent tuning the method (and thinking about initialization) but
  there is never (to our knowledge) a condition in which burn-in time
  is the dominant consideration in choosing an \MCMC\ method.}

Of course, the autocorrelation-time definition
(\ref{eq:autocorrelationtime}) does not by itself provide an
\emph{estimator} for the time. Estimating the auto-correlation time is
notoriously difficult: It is a two-point statistic, and two-point statistics
are much harder to estimate than one-point statistics.\note{See: All of cosmology!}
If you are not a hard-core user of MCMC, and if all you want is heuristic indicators
of convergence, then what you should take from this section is that the auto-correlation
time is involved in variance estimates through \equationname~(\ref{eq:tauvar}) but that
it is hard to estimate.

If you want to think about autocorrelation estimation:\note{One of us (DFM) has written
  much more about autocorrelation estimation in the \project{emcee} documentation
  at \url{http://dfm.io/posts/autocorr}.}
You might first try the na\"ive estimator
\begin{eqnarray}\label{eq:tauestnaive}
\tau &\stackrel{?}{=}& 1 + 2\,\sum_{\Delta = 1}^{N} C(\Delta)
\end{eqnarray}
where the sum is over the autocorrelation function estimated based the chain
using \equationname~(\ref{eq:autocorrelationfn}).
In practice, this is a high variance estimator of the integrated
autocorrelation time and this variance doesn't go to zero for an infinitely
long chain.\note{%
  A.~Sokal has a clear discussion of this topic and several proposals for
  robust autocorrelation time estimation in a set of lecture notes
  \url{http://www.stat.unc.edu/faculty/cji/Sokal.pdf}.}
Instead, we can get a much more robust estimate of the autocorrelation time by
restricting the sum in \equationname~(\ref{eq:tauestnaive}) to $\Delta \le M$
where
$\tau \le M \ll N$
\begin{eqnarray}\label{eq:tauest}
\tau &=& 1 + 2\,\sum_{\Delta = 1}^{M} C(\Delta)
\end{eqnarray}
In practice, $M$ can be chosen iteratively to satisfy these constraints but it
will only be as reliable as the chain itself.
An estimate of $\tau$ using \equationname~(\ref{eq:tauest}) should only be
trusted if the chain is many times ($\sim 100$) longer than $\tau$.\footnote{This
  point is also emphasized at the aforementioned tutorial
  \url{http://dfm.io/posts/autocorr}, where
  a number like 50 is recommended.}

One simple and sensible test of convergence is the Gelman--Rubin
diagnostic \note{\citet{gelmanrubin}.}, which compares the variance
(in one parameter, or your most important parameter, or all
parameters) \emph{within} a chain to the variance \emph{across}
chains.
This requires running multiple chains, and looking at the empirical
variance of the parameter away from its mean within each individual
chain, and comparing it to the variance in the mean of that parameter
across chains, inflated to be a mean per-sample variance.
What Gelman and Rubin do with these variances specifically is
sensible, but the important question of convergence is whether, as the
chains get longer, these two variances asymptotically reach stable
values, and that those two values agree.
The Gelman--Rubin diagnostic is related to the autocorrelation time,
in that it will only deliver success when the chains are much longer
than an autocorrelation time.
It can also be used to assess the accuracy of the chain for performing
integrals---by replacing the mean of the parameter with whatever
integral is of most interest.

@@

\begin{problem}\label{prob:itertau}
Write a peice of code that estiamtes the integrated autocorrelation time for a
chain of samples using an estimate of the autocorrelation function and a given
``window'' size $M$ (see \equationname~\ref{eq:tauest}).
Plot the estimated $\tau$ as a function of $M$ for several contiguous segments
of the chain and overplot the sample function based on the full chain.
What can you conclude from this plot?
Implement an iterative procedure for automatically choosing $M$.\note{%
The recipe given on page 16 of A.~Sokal's notes
(\url{http://www.stat.unc.edu/faculty/cji/Sokal.pdf}) might be helpful.
Note that the definition of $\tau$ in that document is half of the definition
that we use.}
Overplot this estimate on the plot of $\tau(M)$ and the result should look
like \figurename~\ref{fig:itertau}.
\end{problem}

@@

>>>>

Given this pdf $p(\pars)$, we can define \emph{expectation values}
$E_{p(\pars)}[\pars]$
for $\pars$ or for any quantity that can be expressed as a function $g(\pars)$
of $\pars$:
\begin{eqnarray}
E_{p(\pars)}[\pars] &\equiv& \int \pars\,p(\pars)\,\dd \pars
\\
E_{p(\pars)}[g(\pars)] &\equiv& \int g(\pars)\,p(\pars)\,\dd \pars
\quad ,
    \label{eq:the-real-integral}
\end{eqnarray}
where again the integrals are implicitly definite integrals over the
entire domain
of $\pars$ (all the parts of $\pars$ space in which $p(\pars)$ is finite) and the
integrals are multi-dimensional if $\pars$ is multi-dimensional.
These expectation values are the mean values of $\pars$ and $g(\pars)$ under
the pdf.  A good sampling---and really this is the definition of a good
sampling---makes the sampling approximation to these integrals
accurate.
With a good sampling $\setof{\pars_k}_{k=1}^K$ the integrals get replaced
with sums over samples $\pars_k$:
\begin{eqnarray}
E_{p(\pars)}[\pars] &\approx& \frac{1}{K}\,\sum_{k=1}^K \pars_k
\\
E_{p(\pars)}[g(\pars)] &\approx& \frac{1}{K}\,\sum_{k=1}^K g(\pars_k)
\quad .
    \label{eq:the-real-samples}
\end{eqnarray}
That is, a sampling is good when any expectation value of interest is
accurately computed via the sampling approximation.
The word ``accurately'' here translates into some kinds of theorems
about limiting behavior; the general idea is that the sampling
approximation becomes exact as $K$ goes to infinity.
The size $K$ of the sampling you need \emph{in practice} will depend
on the expectations you want to compute, and the accuracies you need.

@@

\Needspace{7\baselineskip}
\section{Autocorrelation \& convergence}\label{sec:convergence}%
\nopagebreak%
A key question for an \MCMC\ operator---\emph{the} key question in some
sense---is \emph{how long to run} to be sure of having reliable
results.
It is disappointing and annoying to many that there is no extremely
simple and reliable answer to this question.\note{There is very good
  coverage of most of the points in this \sectionname, and more, in a
  set of lecture notes by Patrick Lam up at
  \url{http://www.people.fas.harvard.edu/~plam/teaching/methods/convergence/convergence_print.pdf}.}

The reason that there is no simple answer is that you can't really
ever know that you have sampled the full posterior pdf, and the reason
for \emph{that} is that if you \emph{could} know that, you would also
be able to solve the famously difficult discrete optimization
problem.\note{Famously, there is ``no free lunch''
  \citep{nofreelunch}: You can't find the global optimum of a general
  optimization problem without exhaustive search of all possibilities.
  This is very closely related---somehow---to the difficulty of sampling.}
Qualitatively, you can consider the scenario where you have two modes---two
separated regions of substantial total probability---in the posterior pdf that
are both important but separated by a large region of low probability.
If you are using a simple sampler, you could sample one of these modes
very well but the sampler will take effectively infinite time to find
the other mode.
In most real problems, the situation is much worse, with an unknown number of
modes, and knowing that you have a complete and representative sampling
is effectively impossible.

@@

The above heuristics can be made more precise in terms of the amount
of deviation one expects between the means and variances, say, of two
disjoint subsets of the chain.
The premier tool for making this heuristic precise, however, is to
look at the \emph{``integrated autocorrelation time''} of the chain.
In general, when one has a sequence $(\pars_1, \pars_2, \theta_3, \cdots)$
generated by a Markov Process in the $\pars$ space, nearby points in
the sequence will be similar, but sufficiently distant points will not
``know about'' one another;
the autocorrelation function measures this.

More formally, as discussed in \sectionname~\ref{sec:sampling}, the goal of
MCMC sampling is to compute integrals of the form given in
\equationname~\ref{eq:the-real-integral} using the Monte Carlo approximation
in \equationname~\ref{eq:the-real-samples}.
The Monte Carlo error introduced by this approximation is proportional to
$\sqrt{\tau_\mathrm{int}/N}$ where $\tau_\mathrm{int}$ is the
integrated autocorrelation time and $N$ is the total number of
samples of $p(\pars)$.
In other words, $\tau_\mathrm{int}$ is the number of steps required for the
chain to produce an \emph{independent} sample.

%The autocorrelation function $C_g$ is defined by
%\begin{eqnarray}
%C_g(\Delta) &\equiv& \frac{E[(g(\pars_k)-\mu_g)\,(g(\pars_{k+\Delta})-\mu_g)]}
%                          {E[(g(\pars)-\mu_g)^2]}
%\label{eq:autocorrelationfn}\\
%\mu_g &=& E[g(\pars)]
%\quad ;
%\end{eqnarray}
%where $g(\pars)$ is a scalar valued function of the parameters, and $\Delta$
%is a lag (difference in index number) between points in the chain.
%In other words, \equationname~(\ref{eq:autocorrelationfn}) is the covariance
%of points in the chain separated by $\Delta$ steps, taken relative to the
%variance.
%In the above equation, the assumption is that the samples $\pars_k$ are
%given in the order that they were generated by the \MCMC\ algorithm.
%By construction
%\begin{eqnarray}
%C_g(0) &=& 1
%\\
%\lim_{\Delta\rightarrow\infty} C_g(\Delta) &=& 0
%\quad ,
%\end{eqnarray}
%and by definition, the autocorrelation ``time'' $\tau$ is
%\begin{eqnarray}
%\tau_g = 1 + 2\,\sum_{\Delta = 1}^{\infty} C_g(\Delta)
%\label{eq:autocorrelationtime}\quad.
%\end{eqnarray}
%Heuristically, the autocorrelation time is the number of samples you
%need to take before you get a new independent sample.
%More precisely, the autocorrelation time is the factor by which you
%have to reduce the number of samples when you compute the variance on
%a sampling-based expectation value estimate.

%That is, if the expectation value $E[g]$ is computed by the sampling
%approximation given in \equationname~(\ref{eq:expectationvalue}),
%there is an uncertainty on that expectation given by
%\begin{eqnarray}
%  \Var[E_{p(\pars)}[g(\pars)]] &=& \frac{\tau_g}{K}\,\Var_{p(\pars)}[g(\pars)]
%  \\
%  &\approx& \frac{\tau_g}{K^2}\,\sum_{k=1}^K \left(g(\pars_k) -
%    E_{p(\pars)}[g(\pars)]\right)^2
%  \quad,
%\label{eq:tauvar}
%\end{eqnarray}
%where we are being a bit loose with terminology because this is the
%variance not on $E_{p(\pars)}[g(\pars)]$ but on our sampling-based
%\emph{estimator} for
%$E_{p(\pars)}[g(\pars)]$, and the $E_{p(\pars)}[g(\pars)]$ inside the sum is
%that estimator too.
%It is slightly off-topic here, but related to this, if you have a long
%chain of length $K$ and with autocorrelation time $\tau$ and you thin
%the chain down to every $\tau$th sample (instead of using all $K$
%samples), you will get just as good sampling-based estimates as if you
%had used all $K$ samples.

%It is also worth noting that there is not just one autocorrelation function or
%autocorrelation time for an \MCMC\ chain.
%Instead, there is an autocorrelation time $\tau_g$ for every function
%$g(\pars)$ and these will, in general, be different.
%Therefore, the autocorrelation time used in \equationname~(\ref{eq:tauvar}) is
%the time computed on the chain of $g(\pars)$ values instead of the
%autocorrelation time for $\pars$.

A sampler with a smaller integrated autocorrelation time is better; you have
to do fewer $f(\pars)$ calls per independent sample, and you have to
run less time to get accurate sampling-based integral estimates.
A sampler that takes an independent sample every time would have an
autocorrelation time of unity, which is the best possible value; this
optimal sampling is only possible for problems where the sampling is
analytic (for example if the posterior is perfectly Gaussian with
known mean and variance).
In general, the best sampler will be different for different problems, and we
will (below; \sectionname~\ref{sec:methods}) tune the samplers we have to do
the best on the problems we have; this tuning will also be problem-specific.
There are many heuristic bases on which different samplers might be
compared or tuned, but fundamentally it is lower autocorrelation time
that separates good samplers from bad ones and is the ultimate basis
on which we compare performance.\note{%
  We sometimes see \MCMC\ methods compared according to burn-in times,
  which, for one, depends strongly on initialization, and, for two,
  depends strongly on tuning and dynamics.  Similarly we often see
  comparisons in terms of acceptance ratio.  In principle the only
  question is how precise are one's inferences given a certain amount
  of computation.  This is set by the autocorrelation time and (pretty
  much) nothing else, for reasonably converged chains.  In the real
  world, of course, one must add to the CPU time the investigator time
  spent tuning the method (and thinking about initialization) but
  there is never (to our knowledge) a condition in which burn-in time
  is the dominant consideration in choosing an \MCMC\ method.}

We won't go into details about how to estimate $\tau_\mathrm{int}$, but it is
notoriously difficult: It is a two-point statistic, and two-point statistics
are much harder to estimate than one-point statistics.\note{See: All of
cosmology!}
If you are not a hard-core user of MCMC, and if all you want is
heuristic indicators of convergence, then what you should take from this
section is that the autocorrelation time is involved in variance estimates,
but that it is hard to estimate.
If you want to think about autocorrelation estimation, more detailed
references can be found elsewhere.\note{%
    A canonical reference is a set of lecture notes by Alan Sokal
    \citep{sokal}.
    Another good reference is a blog post by one of us (DFM) that can be found
    at \url{http://dfm.io/posts/autocorr}.}

%Of course, the autocorrelation-time definition
%(\ref{eq:autocorrelationtime}) does not by itself provide an
%\emph{estimator} for the time. Estimating the auto-correlation time is
%notoriously difficult: It is a two-point statistic, and two-point statistics
%are much harder to estimate than one-point statistics.\note{See: All of cosmology!}
%If you are not a hard-core user of MCMC, and if all you want is heuristic indicators
%of convergence, then what you should take from this section is that the auto-correlation
%time is involved in variance estimates through \equationname~(\ref{eq:tauvar}) but that
%it is hard to estimate.

%If you want to think about autocorrelation estimation:\note{One of us (DFM) has written
%  much more about autocorrelation estimation in the \project{emcee} documentation
%  at \url{http://dfm.io/posts/autocorr}.}
%You might first try the na\"ive estimator
%\begin{eqnarray}\label{eq:tauestnaive}
%\tau &\stackrel{?}{=}& 1 + 2\,\sum_{\Delta = 1}^{N} C(\Delta)
%\end{eqnarray}
%where the sum is over the autocorrelation function estimated based the chain
%using \equationname~(\ref{eq:autocorrelationfn}).
%In practice, this is a high variance estimator of the integrated
%autocorrelation time and this variance doesn't go to zero for an infinitely
%long chain.\note{%
%  A.~Sokal has a clear discussion of this topic and several proposals for
%  robust autocorrelation time estimation in a set of lecture notes
%  \url{http://www.stat.unc.edu/faculty/cji/Sokal.pdf}.}
%Instead, we can get a much more robust estimate of the autocorrelation time by
%restricting the sum in \equationname~(\ref{eq:tauestnaive}) to $\Delta \le M$
%where
%$\tau \le M \ll N$
%\begin{eqnarray}\label{eq:tauest}
%\tau &=& 1 + 2\,\sum_{\Delta = 1}^{M} C(\Delta)
%\end{eqnarray}
%In practice, $M$ can be chosen iteratively to satisfy these constraints but it
%will only be as reliable as the chain itself.
%An estimate of $\tau$ using \equationname~(\ref{eq:tauest}) should only be
%trusted if the chain is many times ($\sim 100$) longer than $\tau$.\footnote{This
%  point is also emphasized at the aforementioned tutorial
%  \url{http://dfm.io/posts/autocorr}, where
%  a number like 50 is recommended.}

Besides estimating the integrated autocorrelation time, another simple and
sensible test of convergence is the Gelman--Rubin
diagnostic,\note{\citet{gelmanrubin}.} which compares the variance (in one
parameter, or your most important parameter, or all parameters) \emph{within}
a chain to the variance \emph{across} chains.
This requires running multiple chains, and looking at the empirical
variance of the parameter away from its mean within each individual
chain, and comparing it to the variance in the mean of that parameter
across chains, inflated to be a mean per-sample variance.
What Gelman and Rubin do with these variances specifically is
sensible, but the important question of convergence is whether, as the
chains get longer, these two variances asymptotically reach stable
values, and that those two values agree.
The Gelman--Rubin diagnostic is related to the autocorrelation time,
in that it will only deliver success when the chains are much longer
than an autocorrelation time.
%It can also be used to assess the accuracy of the chain for performing
%integrals---by replacing the mean of the parameter with whatever
%integral is of most interest.

@@

\begin{problem}\label{prob:itertau}
Write a peice of code that estiamtes the integrated autocorrelation time for a
chain of samples using an estimate of the autocorrelation function and a given
``window'' size $M$ (see \citealt{sokal}).
Plot the estimated $\tau$ as a function of $M$ for several contiguous segments
of the chain and overplot the sample function based on the full chain.
What can you conclude from this plot?
Implement an iterative procedure for automatically choosing $M$.\note{%
The recipe given on page 16 of A.~Sokal's notes \citep{sokal} might be helpful.
Note that the definition of $\tau$ that we adopt is twice the value used by
Sokal.}
Overplot this estimate on the plot of $\tau(M)$ and the result should look
like \figurename~\ref{fig:itertau}.
\end{problem}

@@

\bibitem[Sokal(1997)]{sokal}
    Sokal, A., 1997,
    Monte Carlo methods in statistical mechanics: foundations and new algorithms.
    \textit{Functional integration.}\ 131--192
